data_preparation

### 2024-03-24 gen/paper/paper.Rmd
fixed graph retrieval

---
title: Investigating the influence of genre preferences on movie/series rating patterns
  over time
author: "Team 1 - Timo Philipse, Bram Teunissen, Rodrigo Pačeko Rudzājs, Dian de Ridder
  & Linda van den Boogaart"
output:
  pdf_document: default
  html_document: default
editor_options:
  markdown:
    wrap: 72
---

@@

All assumptions associated with regression were checked via a visual
inspection. Only linearity appeared to be satisfied.

```{r Normality, echo=FALSE, warning=FALSE}
#insert pdf

@@

```{r}
#insert pdf
```

@@

```{r}
#insert pdf
```

@@

```{r}
#insert pdf of results graph with colored dots
```

@@

@@

>>>>

---
title: Investigating the influence of genre preferences on movie/series rating patterns
  over time
author: "Team 1 - Timo Philipse, Bram Teunissen, Rodrigo Pačeko Rudzājs, Dian de Ridder & Linda van den Boogaart"
output: pdf_document
editor_options:
  markdown:
    wrap: 72
---

@@

All assumptions associated with regression were checked via a visual
inspection. Only normality appeared to be satisfied.

```{r echo=FALSE, warning=FALSE}
library(knitr)

knitr::include_graphics("../../gen/data_preparation/qq_normality.png")

@@

```{r echo=FALSE}
knitr::include_graphics("../../gen/data_preparation/homoskedacity.png")
```
```{r echo=FALSE}
knitr::include_graphics("../../gen/data_preparation/independence.png")
```

@@

```{r echo=FALSE}
knitr::include_graphics("../../gen/data_preparation/linearity.png")
```

@@

@@

```{r echo=FALSE}
knitr::include_graphics("../../gen/data_analysis/results_plot.png")
```

@@

```{r saving}
library(rmarkdown)

render(input = "../../gen/paper/paper.Rmd",
       output_format = "pdf_document",
       output_file = "../../gen/paper/paper.pdf")
```

### 2024-03-24 src/analysis/regression_analysis.Rmd
fixed graph retrieval

# Let's run our analysis! 
## And see how genre preferences as inferred from average ratings evolve over time

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(fixest)
library(tidyr)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
```

Let's start with loading the data 
```{r include=FALSE}
mdc <- read_csv("../../data/movie_data_cleaned.csv")
```

@@

```{r skeleton model, echo=FALSE}
simple_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news,
                      data = mdc,
                      split = ~ slide_window_5)
summary(simple_model)
```
So we now have the most basic form of a regression to work with. If you click around a bit you see that within the 5 year time windows some genres become significant, others stay significant and some become insignificant. However, this is the most basic form of a regression and correlational at best. Therefore we are going to extent this formula a bit and see how it evolves to something that may become a little more causal.

@@

```{r echo=FALSE}
fixed_type_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
                                data = mdc,
                                split = ~ slide_window_5)

summary(fixed_type_model)
```

@@

```{r echo=FALSE}
etable(simple_model)
```

```{r echo=FALSE}
etable(fixed_type_model)
```

@@

```{r include=FALSE}
fixed_tt_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
                                data = mdc,
                                split = ~ slide_window_5)
```

@@

```{r assumptions, echo=FALSE}

@@

```{r plotting results}
#getting the coefficients
list_of_coeficients <- coef(fixed_tth_model)
#getting
list_of_standard_deviations <- se(fixed_tth_model)

@@

ggplot(graph_data, aes(x = sample, y = coef_value, color = factor(p_significance))) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  scale_color_manual(values = c("red", "green")) +
  xlab("Estimates") + ylab("Years") +
  facet_wrap(~ genre)

```

```{r saving the doc}
#insert pdf knit path
```

>>>>

---
title: "regression analysis"
author: "Team 1 Data Prep"
date: "2024-03-24"
output: pdf_document
---

# Let's run our analysis! 
## And see how genre prefferences as inferred from average ratings evolve over time

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(fixest)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
library(rmarkdown)
```

Let's start with loading the data 
```{r retrieving data, include=FALSE}
mdc <- read_csv("../../data/movie_data_cleaned.csv")
```

@@

```{r skeleton model, echo=FALSE}
simple_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news,
                      data = mdc,
                      split = ~ slide_window_5)
etable(simple_model)
```
So we now have the most basic form of a regression to work with. If you click around a bit you see that within the 5 year time windows some genres become significant, others stay significant and some become insignificant. However, this is the most basic form of a regression and correlational at best. Therefore we are going to extent this formula a bit and see how it evolves to something that may become a little more causal.

@@

```{r skeleton model + titleType fixed effect, echo=FALSE, warning=FALSE}
fixed_type_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
                                data = mdc,
                                split = ~ slide_window_5)

etable(fixed_type_model)
```

@@

@@

```{r model + clustered errors, include=FALSE}
fixed_tt_model <- feols(averageRating ~ drama + romance + war + crime + thriller+ history + comedy + fantasy + adventure + mystery + biography + action + scifi + western + horror + sport + documentary + musical + filmnoir + animation + adult + gameshow + realitytv + talkshow + short + news | titleType,
                                data = mdc,
                                split = ~ slide_window_5)

etable(fixed_tt_model)
```

@@

```{r model + hetrogeinity adjustement, echo=FALSE}

@@

```{r plotting results, echo=FALSE}
#getting the coefficients
list_of_coeficients <- coef(fixed_tth_model)
#getting
list_of_standard_deviations <- se(fixed_tth_model)

@@

results_plot <- ggplot(graph_data, aes(x = sample, y = coef_value, color = factor(p_significance))) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
  scale_color_manual(values = c("red", "green")) +
  xlab("Estimates") + ylab("Years") +
  facet_wrap(~ genre) + theme_minimal()

ggsave("../../gen/data_analysis/results_plot.png", results_plot)

results_plot
```
As you can see from the plot some genres, such as romance, are largely significant are nicely consistent over the years. However, genres such as game-shows or news (which only rose after the 2000's) do not have observations for all years and the observations that are there are remarkably volatile given their large confidence intervals.

Additionally, some genres are never significant, e.g., sports and thriller. While others become significant and never stop, e.g., history. There are also speaks in genres like war, where it seems to be falling in and out of favor.

```{r saving the doc}
render("../../src/analysis/regression_analysis.Rmd",
       output_format = "pdf_document",
       "../../gen/data_analysis/regression_analysis.pdf")
```

### 2024-03-24 src/data_prep/data_prep.Rmd
fixed graph retrieval

@@

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(tidyr)
library(dplyr)
library(stringr)
```

```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
movie_data <- read_csv("movie_data.csv")

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
distribution_of_average_ratings_unrounded <- ggplot(movie_data, aes(x = averageRating)) +
  geom_histogram(binwidth = 0.1, fill = "orange", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, by = 0.5), limits = c(0, 10), labels = scales::number_format(accuracy = 0.1)) +
  labs(x = "averageRating", y = "Frequency") +
  theme_minimal()

@@

```{r Plot DV and numVotes, echo=FALSE, message=FALSE, warning=FALSE}
distribution_of_number_of_votes <- ggplot(movie_data, aes(x = numVotes)) +
  geom_dotplot(fill = "darkorange", color = "black", binwidth = 500) +
  labs(title = "Distribution of numVotes",
       x = "Number of Votes", y = "Frequency") + 
  theme_minimal()

@@

```{r Filtering DV, echo=FALSE, message=FALSE, warning=FALSE}
below_100 <- movie_data %>%
  select(numVotes) %>%
  filter(numVotes < 100)

@@

```{r echo=FALSE}
number_of_votes_vs_average_rating <- ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
  geom_point() + 
  facet_wrap(~genres)

@@

Let's see how the actual ratings are then distributed across genres
```{r echo=FALSE}
number_of_votes_distributions_per_genre <- ggplot(movie_data, aes(averageRating, color= genres))+
  geom_bar() +
  facet_wrap(~genres)

@@

```{r echo=FALSE}
qq_normality <- ggplot(movie_data, aes(sample = averageRating, color = genres)) +
  stat_qq() +
  facet_wrap(~genres)

@@

```{r echo=FALSE}
residuals <- movie_data$averageRating - mean(movie_data$averageRating)
fitted_values <- movie_data$averageRating

@@

```{r echo=FALSE}
# Calculate residuals
residuals <- movie_data$averageRating - mean(movie_data$averageRating)

@@

Linearity looks chaotic but okay. It may be a little smaller on the left and increases to the right but this is very little. So we move on the last assumption, linearity. This is tricky, because there is no reason for genre to lead to a higher or lower rating. This is really specific to the watcher and also how the movie/series are doing. But when we add the time variable it can be that there is a relation between these elements, albeit unlikely to be linear.

```{r echo=FALSE}
linearity <- ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
  geom_point() +
  facet_wrap(~genres)

@@

```{r include=FALSE}
movie_data <- movie_data %>%
  mutate(genre_dummy = 1) %>%
  pivot_wider(names_from = genres, values_from = genre_dummy, values_fill = list(genre_dummy = 0)) %>%
   rename(
    scifi = `sci-fi`,
    filmnoir = `film-noir`,
    gameshow = `game-show`,
    realitytv = `reality-tv`,
    talkshow = `talk-show`
  )
```
After all the filtering, we have 70087 films left in our data set. From this number, 60246 are movies and 9841 are series. The resulting standard deviation for the total of films is 1.12. 
In the period from 2015 until 2019, the most amount of films were released being 11353, 2019 was the year with the biggest amount of releases, 2586 films. On the other hand, 1926 the least amount of films were released on IMDB, 54 films. 
The average number of votes in the final dataset was 7146.
In terms of runtime, the films are on average 101 minutes long.
The average ratings of the films in our final data set is 6.3, the lowest rating noted as 1 and the highest as 10.

@@

```{r save file}
write_csv(movie_data, "data/movie_data_cleaned.csv")
```

>>>>

---
title: "data_preparation"
author: "Team 1 Data Prep"
date: "2024-03-24"
output: pdf_document
---

@@

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(tidyr)
library(dplyr)
library(stringr)
library(rmarkdown)
```

```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
movie_data <- read_csv("../../data/movie_data.csv")

@@

```{r distribution_of_average_ratings_unrounded, echo=FALSE, message=FALSE, warning=FALSE}
distribution_of_average_ratings_unrounded <- ggplot(movie_data, aes(x = averageRating)) +
  geom_histogram(binwidth = 0.1, fill = "orange", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, by = 0.5), limits = c(0, 10), labels = scales::number_format(accuracy = 0.1)) +
  labs(x = "averageRating", y = "Frequency") +
  theme_minimal()

@@

```{r distribution_of_number_of_votes, echo=FALSE, message=FALSE, warning=FALSE}
distribution_of_number_of_votes <- ggplot(movie_data, aes(x = numVotes)) +
  geom_dotplot(fill = "darkorange", color = "black", binwidth = 500) +
  labs(title = "Distribution of numVotes",
       x = "Number of Votes", y = "Frequency") + 
  theme_minimal()

@@

```{r distribution_of_number_of_votes_below_10, echo=FALSE, message=FALSE, warning=FALSE}
below_100 <- movie_data %>%
  select(numVotes) %>%
  filter(numVotes < 100)

@@

```{r number_of_votes_vs_average_rating, echo=FALSE}
number_of_votes_vs_average_rating <- ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
  geom_point() + 
  facet_wrap(~genres)

@@

Let's see how the actual ratings are then distributed across genres
```{r number_of_votes_distributions_per_genre, echo=FALSE}
number_of_votes_distributions_per_genre <- ggplot(movie_data, aes(averageRating, color= genres))+
  geom_bar() +
  facet_wrap(~genres)

@@

```{r qq_normality, echo=FALSE}
qq_normality <- ggplot(movie_data, aes(sample = averageRating, color = genres)) +
  stat_qq() +
  facet_wrap(~genres)

@@

```{r homoskedacity, echo=FALSE}
residuals <- movie_data$averageRating - mean(movie_data$averageRating)
fitted_values <- movie_data$averageRating

@@

```{r independence, echo=FALSE}
# Calculate residuals
residuals <- movie_data$averageRating - mean(movie_data$averageRating)

@@

Indepdence looks chaotic but okay. It may be a little smaller on the left and increases to the right but this is very little. So we move on the last assumption, linearity. This is tricky, because there is no reason for genre to lead to a higher or lower rating. This is really specific to the watcher and also how the movie/series are doing. But when we add the time variable it can be that there is a relation between these elements, albeit unlikely to be linear.

```{r linearity, echo=FALSE}
linearity <- ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
  geom_point() +
  facet_wrap(~genres)

@@

```{r include=FALSE}
movie_data <- movie_data %>%
  mutate(genre_dummy = 1) %>%
  pivot_wider(names_from = genres, values_from = genre_dummy, values_fill = list(genre_dummy = 0)) %>%
   rename(
    scifi = `sci-fi`,
    filmnoir = `film-noir`,
    gameshow = `game-show`,
    realitytv = `reality-tv`,
    talkshow = `talk-show`
  )
```

After all the filtering, we have 70087 films left in our data set. From this number, 60246 are movies and 9841 are series. The resulting standard deviation for the total of films is 1.12. 
In the period from 2015 until 2019, the most amount of films were released being 11353, 2019 was the year with the biggest amount of releases, 2586 films. On the other hand, 1926 the least amount of films were released on IMDB, 54 films. 
The average number of votes in the final dataset was 7146.
In terms of runtime, the films are on average 101 minutes long.
The average ratings of the films in our final data set is 6.3, the lowest rating noted as 1 and the highest as 10.

@@

```{r save file, echo=TRUE}
write_csv(movie_data, "../../data/movie_data_cleaned.csv")
```
